---
title: "Course Project"
author: "Margerys Salgado"
date: "10/6/2019"
output:

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## About the Course Project

This peer assessed assignment has two parts. 
First, you will create a Shiny application and deploy it on Rstudio's servers. 
Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

Your Shiny Application:

1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
2. Deploy the application on Rstudio's shiny server
3. Share the application link by pasting it into the provided text box
4. Share your server.R and ui.R code on github

## How to use the application
This application predicts the horsepower of a car given the fuel efficiency in miles per gallon for the car.

## Dataset
```{r summary}
rm(list=ls())

library(ggplot2)
library(plotly)

data(cars)
summary(cars)

```

## Plot
In the scatterplot below are represented the data used for the prediction model
```{r plot}
p <- ggplot(data=cars, aes(speed, dist)) + 
  geom_point(stat = "identity") +
  theme_minimal()

ggplotly(p)
```

## Reactive App
```{r, comment="", warning=F, message=F, echo=T}
library(shiny)

shinyUI(fluidPage(
  titlePanel("Predict Horsepower from MPG"),
  sidebarLayout(
    sidebarPanel(
      sliderInput("sliderMPG", "What is the MPG of the car?", 10, 35, value=20),
      checkboxInput("ShowModel1", "Show/Hide Model1", value = TRUE),
      checkboxInput("ShowModel2", "Show/Hide Model2", value = TRUE)
    ),
    mainPanel(
      plotOutput("Plot1"),
      h3("Predicted Horsepower from Model1:"),
      textOutput("pred1"),
      h3("Predicted Horsepower from Model2:"),
      textOutput("pred2")
    )
  )
))
      
```

